### 2015-12-21 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Update Equipment Guide
Updated Equipment_and_Testing_Guide with necessary step for setting up arduino data logger

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Keith M. Stakes \\
Roy A. McLane \\
Jay A. McElroy \\
Daniel Madrzykowski \\
\bigskip
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

@@

\begin{enumerate}
\item Install RabbitMQ for your platform and start the RabbitMQ server (./sbin/rabbitmq-server on Mac or Linux).
https://www.rabbitmq.com/
\item Copy the receive\_data.py script from the NIST-FIRE repository to the data logging computer.
\item Install Python (The Anaconda Python distribution from Continuum Analytics is recommended)
\item Install the pika module for Python using
\begin{verbatim}
pip install pika
\end{verbatim}
\item Run the receive\_data.py script as
\begin{verbatim}
python receive_data.py 192.168.1.100 output.csv
\end{verbatim}
\end{enumerate}

>>>>

\headerC{
\flushright{
Roy A. McLane \\
Craig G. Weinschenk \\
Keith M. Stakes \\
Kristopher J. Overholt \\
Daniel Madrzykowski \\

\bigskip
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

@@

\begin{enumerate}
\item Install RabbitMQ for your platform and start the RabbitMQ server (./sbin/rabbitmq-server on Mac or Linux).
https://www.rabbitmq.com/
\item Create .config file 
    \begin{itemize}
    \item Open \textit{rabbitmq.config.example} (./etc/rabbitmq/ on Mac/Linux; ./etc/ on Windows)
    \item Add `[ \{loopback\_users, [] \}' after the `\{rabbit,' line and save file as `rabbitmq.config' in the directory containing the example file \\
    \textit{Note:} On Windows, may have to save it in the directory \\
    `C:\textbackslash Users/\%USERNAME\%/AppData/Roaming/RabbitMQ/' \\
    To find such directory, search `rabbitmq.config.example' on computer and open approriate file location.
    \end{itemize}
\item Copy the receive\_data.py script from the NIST-FIRE repository to the data logging computer.
\item Install Python (The Anaconda Python distribution from Continuum Analytics is recommended)
\item Install the pika module for Python using
\begin{verbatim}
pip install pika
\end{verbatim}
\item Run the receive\_data.py script as
\begin{verbatim}
python receive_data.py 192.168.1.100 output.csv
\end{verbatim}
\end{enumerate}
